Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species

### 2024-08-31 ms.qmd
Updates

Table 1. Estimates of Reversal learning slope for all the different treatments per each task, specie, and group. Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All pmcmc tested the hypothesis that the mean equals zero. In bold, those values that are significant (pmcmc <0.05).

@@

```{r, fig_rawdata}
#| label: fig_rawdata
#| fig.cap: "Raw data for the reversal tasks for both species. Lines represent the mean proportion of correct choices per trial for each treatment."
#
# Load the data
data_raw <- clean_df %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
        species = factor(species,
          levels = c("delicata", "guichenoti"),
          labels = c("italic('L. delicata')", "italic('L. guichenoti')"))) %>%
data.frame()
#
# Plot the raw data for the reversal tasks for both species
plot_raw <- ggplot(data_raw, aes(x = trial_reversal, y = FC_reversal, color = trt, fill = trt)) +
  geom_smooth(method = "loess", linewidth = 1, alpha = 0.1) +
  scale_color_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
  scale_fill_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
  facet_wrap(~species, nrow = 1, labeller = label_parsed) +
  labs(x = "Trial", y = "Proportion of correct choices", color = "Treatments", fill = "Treatments") +
  theme_classic()
#
# Save the plot
ggsave("./output/figures/plot_raw.png", plot=plot_raw, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/plot_raw.png")
```

>>>>

Table 1. Estimates of Reversal learning slope for all the different treatments per each task, specie, and group. Mean shows the arithmetic means of the estimates obtained from the posteriors of the model, and 95% CI indicates the 95% confidence interval of the mean. All pmcmc tested the hypothesis that the mean equals zero. In bold, those values that are significant (p~mcmc~ <0.05).

@@

```{r, fig_rawdata}
#| label: fig_rawdata
#| fig.cap: "Probability of choosing correctly over trials for each of the treatments and species. The dots represent the proportion of individuals per trial that chose correctly while the lines show the mean predicted probability of choosing correctly, estimated using the posteriors of our model."
#
# Load the data
data_raw <- clean_df %>%
  group_by(species, trt, trial_reversal) %>%
  summarize(prop_correct = mean(FC_reversal, na.rm = TRUE)) %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
        species = factor(species,
          levels = c("delicata", "guichenoti"),
          labels = c("italic('L. delicata')", "italic('L. guichenoti')"))) %>%
  rename(Trial = trial_reversal,
         Treatment = trt) %>%
data.frame()
#
# Get the df for the predicted prob
df_deliprob$species <- "italic('L. delicata')"
df_guichprob$species <- "italic('L. guichenoti')"
df_combined <- rbind(df_deliprob, df_guichprob)
df_all <- full_join(df_combined, data_raw, by = c("Trial", "Treatment", "species"))
# Plot the raw data for the reversal tasks for both species with the predicted prob
plot_raw <- ggplot(data = df_all, aes(x = Trial, y = Mean_Predicted_prob, color = Treatment, fill = Treatment)) +
  geom_smooth(linewidth = 1) +
  geom_point(data = df_all, aes(x = Trial, y = prop_correct, color = Treatment, fill = Treatment)) +
  scale_color_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
  scale_fill_manual(values = c("darkblue", "#68bde1", "#b50101", "#fa927d")) +
  facet_grid(species ~ Treatment, labeller = label_parsed, switch = "y") +
  labs(x = "Trial", y = "Proportion of correct choices", color = "Treatments", fill = "Treatments") +
  theme_classic()
#
# Save the plot
ggsave("./output/figures/plot_raw.png", plot=plot_raw, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/plot_raw.png")
```
